% cv de Rainan Miranda de Jesus
%Email : rainan.jesus@pm.me

\documentclass[margin,line]{res}
\usepackage[utf8]{inputenc}
\usepackage[portuguese]{babel}
\usepackage{graphicx}
\graphicspath{ {assets/} }
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdfpagemode=FullScreen,
    }

\newenvironment{list1}{
 \begin{list}{\ding{113}}{%
     \setlength{\itemsep}{0in}
     \setlength{\parsep}{0in} \setlength{\parskip}{0in}
     \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
     \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
 \begin{list}{$\bullet$}{%
     \setlength{\itemsep}{0in}
     \setlength{\parsep}{0in} \setlength{\parskip}{0in}
     \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
     \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Rainan Miranda de Jesus \vspace{0.2cm} \vspace*{.1in}}
\vspace{0.2cm}
\begin{resume}
\section{Personal Info}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{3.5in}}
{\it Address: }                   & {\it Birth Date:}  10/09/1996 \\
Av. Oeste, QD 19 LT 24 & {\it Phone:}  (71) 98691-0699 \\
Camaçari, BA            & {\it E-mail:}  \href{mailto:rainan.jesus@pm.me}{rainan.jesus@pm.me}\\
Brasil                      & {\it }\\
{\it GitHub:}  & {\it LinkedIn:} \\
\href{https://github.com/rainanDeveloper}{https://github.com/rainanDeveloper} & \href{https://www.linkedin.com/in/rainan-miranda-de-jesus-508a43153/}{https://www.linkedin.com/in/rainan-miranda-de-jesus-508a43153/}
\end{tabular}
\vspace{0.2cm}
\section{Education}
\begin{list2}

\item Technical Course in Informatics at IFBA Campus Camaçari, ending in June 2018.
\end{list2}
\section{Personal Projects}
\begin{list2}
\item Mercury App (https://github.com/rainanDeveloper/MercuryApp)

    MVP of sending messages with asymmetric encryption and diffie-hellman implementation.
\item Bluetools (https://github.com/rainanDeveloper/bluetools-v2)

    MVP of a minimal enterprise management system (ERP).
\item Learnsky (https://github.com/rainanDeveloper/learnsky)

    Simple quiz sample project on knowledge in astronomy (name of stars)
\end{list2}
\vspace{0.2cm}
\section{Experience}
\begin{list2}
\item Intern at IFBA Campus Camaçari, where he was responsible for the creation of the Undergraduate Computer Site. Duration: months.

    Responsible for the development of the undergraduate computing site, which was developed in PHP, with HTML, CSS and Javascript.

\item Intern at Clariontec Sistemas. Duration: 1 year and 6 months

	Responsible for developing several internal tools on the company.
	
	Relevant technologies used: PHP, MySQL

\item FullStack Entry-level Developer at Clariontec Sistemas - CLT Hiring. Duration: 1 year and 11 months.

    Responsible for the development of several applications (backend, frontend, desktop, etc). Developed Desktop applications using a low code tool called Windev.

    Relevant technologies used: PHP, HTML, CSS, Javascript, NodeJS, MySQL, C\#, .NET.

    Had learned a lot about SQL, given that much of the business rules of various applications were in the database (usually MySQL), and was very rare the use of ORM's.

\item Entry-level Backend Developer at Blockhub Tecnologia - PJ Hiring. Duration: 1 year

    Responsible for the development of several API's.

    Technologies used: NodeJS, MongoDB, Typescript, NestJS.

\item Mid-Level Backend developer at Foursys, on Bradesco Bank's team. Start: 12/2022, until now

	Responsible for developing the BFF´s (Backend for frontend api's) of the main app of Bradesco using nodejs, typescript and axios.
	
	Technologies used: Docker, Nodejs, Typescript, Axios

\end{list2}
\vspace{0.2cm}
\section{Idioms}
\begin{list2}
\item English - Understands Well, Speaks Reasonably, Reads Well, Writes Well.
\end{list2}
\vspace{0.2cm}
\section{Computing skills}
\begin{list2}
\item Frontend skills: HTML 5, CSS3, ReactJS (Framework js), Javascript ES6

\item Languages: C, .NET, Javascript (NodeJS), Typescript, C\#

\item Frameworks: Express, NestJS, TypeORM, Sequelize

\item Technologies: NodeJS, MySQL, Redis, Postgres (basic knowledge), MongoDB (basic knowledge)

\item DevOps skills: Docker, Linux, Nginx
\end{list2}
\end{resume}
\end{document}